---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stadlColorPaletteR

<!-- badges: start -->
<!-- badges: end -->

The goal of stadlColorPaletteR is to provide easy functions to create your own color platttes to be used in ggplot.

## Installation

You can install the development version of stadlColorPaletteR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thgsponer/stadlColorPaletteR")
```

## Documentation

Full documentation website on: https://thgsponer.github.io/stadlColorPaletteR

## Example

This is a basic example which shows you how to create a color palette. First, lets define some colors as the basis for our palettes.

```{r base-colors}
library(stadlColorPaletteR)
library(ggplot2)
library(tidyverse)

set.seed(123)
mycolors <- tibble(color_names = sample(colors(),5), 
                   hex_code = colorRampPalette(color_names)(length(color_names)))

mycolors
```

Now we generate all possible combinations of these colors.

