---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(dplyr)
library(magrittr)
library(readr)
library(ggplot2)
library(scales)
library(ggpubr)
library(utils)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below

# set.seed(123)
# mycolors <- tibble(color_names = sample(colors(),5), 
#                    hex_code = colorRampPalette(color_names)(length(color_names)))
datafile <- system.file("mycolors.csv", 
                        package = "stadlColorPaletteR")
mycolors <- readr::read_csv(datafile)

```


# Functions to generate color palettes


## Extract hex-code of colors specified in a tibble

```{r function-get_color_hex_code}
#' Get hex code of colors
#'
#' @param ... Names of colors as character 
#' @param base_colors A tibble with color_names and hex_codes as columns
#'
#' @return
#' Hex code of colors specified
#' 
#' @export
#'
#' @examples
get_color_hex_code <- function(..., base_colors) {

  cols <- c(...)
  if (is.null(cols))
    return (base_colors %>% dplyr::pull(hex_code))
  if (!all(cols%in%base_colors$color_names)){
    not <- cols[!cols%in%base_colors$color_names]
    warning(paste(not, collapse=', '), 
            ' not part of base_colors!')
  }
    
  base_colors %>% 
    dplyr::filter(
      color_names %in% cols) %>% 
    dplyr::pull(hex_code)
}
```

```{r examples-get_color_hex_code}
datafile <- system.file("mycolors.csv", 
                        package = "stadlColorPaletteR")
mycolors <- readr::read_csv(datafile)
get_color_hex_code('palevioletred2', base_colors = mycolors)

```

```{r tests-get_color_hex_code}

test_that("get_color_hex_code works properly and show error if needed", {
  set.seed(123)
  myc <- tibble(color_names = sample(colors(),5), 
                     hex_code = colorRampPalette(color_names)(length(color_names)))
  
  expect_true(get_color_hex_code('mediumorchid1', base_colors = myc) == '#E066FF')
  expect_warning(get_color_hex_code("fuchsia", base_colors = myc), 'fuchsia not part of base_colors')
  expect_error(get_color_hex_code("mediumorchid1", base_colors = asdf), "object 'asdf' not found")
})

```

## Generate colors for later interpolation

```{r function-generate_colors_to_interpolate}
#' Generate all possible combination of n colors from the total number N of colors provided. Will be used later for interpolation. 
#'
#' @param colors A tibble with color_names and hex_codes as columns. 
#' @param n An integer between 1 and number of colors provided.
#'
#' @return
#' A list of length C(N,n), each element containing n colors, where C(N,n) denotes the number of n-combination from a set of N elements. 
#' 
#' @export
#'
#' @examples
generate_colors_to_interpolate <- function(colors, n){
  if(n<1) {
    stop("n must be greater than 1")
  }
  pal <- combn(get_color_hex_code(base_colors = colors),n)
  colnames(pal) <- paste('pal',1:ncol(pal), sep = '')
  as.list(
    as.data.frame(pal)
  )
}
```

```{r examples-generate_colors_to_interpolate}
datafile <- system.file("mycolors.csv", 
                        package = "stadlColorPaletteR")
mycolors <- readr::read_csv(datafile)

# combinations with 2 colors
generate_colors_to_interpolate(mycolors, 2)

#combinations with all colors
generate_colors_to_interpolate(mycolors, nrow(mycolors))

```

```{r tests-generate_colors_to_interpolate}

  set.seed(123)
  myc <- tibble(color_names = sample(colors(),5), 
                     hex_code = colorRampPalette(color_names)(length(color_names)))
  
  p2 <- combn(get_color_hex_code(base_colors = myc),2)
  colnames(p2) <- paste('pal',1:ncol(p2), sep = '')
  p2 <- as.list(
    as.data.frame(p2)
  )

  p1 <- generate_colors_to_interpolate(colors = myc, 2)
  
  testthat::expect_true(
    identical(p1, p2)
  )
  
  testthat::expect_error(generate_colors_to_interpolate(colors = myc, 0), 
               "n must be greater than 1")

  testthat::expect_error(generate_colors_to_interpolate(colors = myc, 0))
  
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

## Use sub-functions in the same chunk

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
